{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-22 draft.tex
Comments Answered in the Introduction Section

{\it Burak: It isn't clear what you're getting at here} Learning
an object-specific classifier in an online manner can better handle
challenging scenarios with the cost of increased complexity.

@@

@@

>>>>

{\it Burak: It isn't clear what you're getting at here}

{\it YoungWoo : Here, I am making an introduction
into the tracking-by-detection paradigm. I wanted to explain that they improve tracking as they learn an appearance model representative of the background and object. However, as I want to point out, the tracking-by-detection algorithms can be unfeasible as training a robust classifier can be costly. } Learning
an object-specific classifier in an online manner can better handle
challenging scenarios with the cost of increased complexity.

@@

{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges. I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122. Do you think it makes sense? This way, we give an introduction on tracking-by-detection.}

@@

{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF. We can probably combine them in a single paragraph followed by our contributions.}
